\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-20 ms/adult.tex
Update data writeup + visits results

@@

We code pornographic content at the domain level. Our main analysis depends on the domain classifications that come with YouGov data (see \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains). In the Appendix, we use a keyword classifier and a machine learning classifier. As you will see, all of these methods consistently show the same thing. All of this ignores pornography available via more conventional channels. For instance, some pornography is consumed on sites like Tumblr.

@@

%=============================================
% Figure for concentration of porn consumption
%=============================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Porn Sites}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
		Time units is hours.
		Data is at the panelist-domain level.
		Others indicate traffic to all other adult sites outside of the top 10.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption}
\end{figure}

@@

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Porn Sites by Party}
	\includegraphics[width=.7\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}

@@

%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}cc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

%=====================================================================
% Tabulated percentiles of proportion of duration spent on adult sites
%=====================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites}
	\label{tab:distribution_prop_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}cc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_prop_duration} for the plot.
	}
\end{table}

%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party}
	\label{tab:distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\label{tab:distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

@@

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_duration_nonzeroes_covariates}
\end{figure}
\FloatBarrier
%===============================================================================
% Analogous results for visits to adult sites
%===============================================================================
\section{Analyses of Visits}

>>>>

Overall, we have over 6 million web browsing records by the 1,200 individuals over the one-month period of June 2022. 
For each web browsing activity, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain. Individuals are spread out over the US states and regions (see \cref{fig:map_duration}). 
Our data also comes with characteristics for the 1,200 individuals.
We have information on their party identification, which we use to code their partisanship.
We verify this using information on whether they voted for the Republican or Democratic candidate in the 2020 presidential election.
Most individuals reported their party identification, with 120 individuals who did not respond or say not sure/don't know.
Out of the 1,080 individuals who report party identification, the majority 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent.
In the analyses focusing on splits by party, we use only those who lean either Republican or Democrat.
We also have information on birth year, gender, race, and education level.
\cref{tab:characteristics_split_by_party} shows differences in gender, and race(?) by party. 
Hence, our analyses below for differences in porn consumption includes these characteristics in the estimation.

@@

We code pornographic content at the domain level. 
Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as porn sites. 
These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com). 
A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites.
See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains.
Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites. For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We manually check the top adult domains in our sample to remove obvious false positives. Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}
In the Appendix, we use a keyword classifier and a machine learning classifier. As you will see, all of these methods consistently show the same thing. All of this ignores pornography available via more conventional channels. For instance, some pornography is consumed on sites like Tumblr.

@@

%=============================================
% Figure for concentration of porn consumption
%=============================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Porn Sites}
	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
		Time units is hours.
		Data is at the panelist-domain level.
		Others indicate traffic to all other adult sites outside of the top 10.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption}
\end{figure}

@@

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Porn Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}

@@

%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

%=====================================================================
% Tabulated percentiles of proportion of duration spent on adult sites
%=====================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites}
	\label{tab:distribution_prop_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_prop_duration} for the plot.
	}
\end{table}

%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party}
	\label{tab:distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\label{tab:distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

@@

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_duration_nonzeroes_covariates}
\end{figure}
\FloatBarrier

%===============================================================================
%===============================================================================
% Analogous results for visits to adult sites
%===============================================================================
%===============================================================================
\section{Analyses of Visits}
%=================================================
% Figure for Distribution of visits to adult sites
%=================================================
\begin{figure}[ht]
	\centering
	\caption{Distribution of Traffic to Pornography Online}
	\includegraphics[width=.5\linewidth]{../figs/distribution_visits_to_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows the number of visits to adult sites by individuals who consumed pornography in the sample period.
		Individuals are split into deciles with each bin containing approximately the same number of individuals.
		Height of bars indicate mean of each bin.
		Capped vertical bars are 95\% confidence intervals.
		See \cref{tab:distribution_visits} for the more tabulated values.
	}
	\label{fig:distribution_visits}
\end{figure}

%===============================================================
% Figure for Distribution of proportion of visits to adult sites
%===============================================================
\begin{figure}
	\centering
	\caption{Percentage of Traffic to Pornography Online}
	\includegraphics[width=.5\linewidth]{../figs/distribution_proportion_visits_to_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows the proportion of visits to adult sites by individuals who consumed pornography in the sample period.
		Individuals are split into deciles with each bin containing approximately the same number of individuals.
		Height of bars indicate mean of each bin.
		Capped vertical bars are 95\% confidence intervals.
		See \cref{tab:distribution_prop_visits} for the more tabulated values.
	}
	\label{fig:distribution_prop_visits}
\end{figure}

%==========================================
% Splits by party for visits to adult sites
%==========================================
\begin{figure}
	\centering
	\caption{Distribution of Traffic to Pornography Online by Party}
	\includegraphics[width=.55\linewidth]{../figs/distribution_visits_to_adultsites_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows splits by party and by percentiles for visits to adult sites for panelists in the sample who consumed pornography in the sample period.
		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
		The \emph{x} symbols indicate actual panelists based on their percentiles.
		See \cref{tab:distribution_visits_party} for the more tabulated values.
	}
	\label{fig:distribution_visits_party}
\end{figure}

%========================================================
% Splits by party for proportion of visits to adult sites
%========================================================
\begin{figure}
	\centering
	\caption{Percentage of Traffic to Pornographic Sites by Party}
	\includegraphics[width=.55\linewidth]{../figs/distribution_proportion_visits_to_adultsites_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows splits by party and by percentiles for visits to adult sites for panelists in the sample who consumed pornography in the sample period.
		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
		The \emph{x} symbols indicate actual panelists based on their percentiles.
		See \cref{tab:distribution_prop_visits_party} for the more tabulated values.
	}
	\label{fig:distribution_prop_visits_party}
\end{figure}

%===============================================
% Tabulated percentiles of visits to adult sites
%===============================================
\begin{table} \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Traffic to Pornography Online}
	\label{tab:distribution_visits}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_visits_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for traffic to porn sites by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_visits} for the plot.
	}
\end{table}

%=============================================================
% Tabulated percentiles of proportion of visits to adult sites
%=============================================================
\begin{table} \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Traffic to Pornographic Sites}
	\label{tab:distribution_prop_visits}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_proportion_visits_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for traffic to porn sites by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_prop_visits} for the plot.
	}
\end{table}

%======================================================================
% Tabulated splits by party and by percentiles for visits to adultsites
%======================================================================
\begin{table} \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Traffic to Pornography Online by Party}
	\label{tab:distribution_visits_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_visits_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for traffic to porn sites by individuals who consumed pornography in the sample period. See \cref{fig:distribution_visits_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table} \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Traffic to Pornographic Sites by Party}
	\label{tab:distribution_prop_visits_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_visits_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for traffic to porn sites by individuals who consumed pornography in the sample period. See \cref{fig:distribution_prop_visits_party} for the plot.
	}
\end{table}

%=======================
% Quantile regressions
% Traffic to adult sites
%=======================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Traffic to Adult Sites by Party}
	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of visits to porn sites by panelists in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_visits_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_visits}
\end{figure}

%=====================================
% Quantile regressions
% Proportion of traffic to adult sites
%=====================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party}
	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_prop_visits}
\end{figure}

%==================================================
% Fig of quantile regression estimates
% Traffic to Adult Sites by Party (with covariates) 
%==================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Traffic to Porn Sites by Party (with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of visits to porn sites by panelists in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_visits} for the same plot without covariates.
	}
	\label{fig:quantile_regression_visits_covariates}
\end{figure}

%===========================================================================
% Fig of quantile regression estimates
% Traffic to Adult Sites by Party (for individuals who consumed pornography)
%===========================================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Traffic to Porn Sites by Party (for individuals who consumed pornography)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of visits to porn sites by panelists in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_visits} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_visits_nonzeroes}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Traffic to Porn Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of visits to porn sites by panelists in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_visits_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_visits_nonzeroes_covariates}
\end{figure}

%=============================================================
% Fig of quantile regression estimates
% Percentage Traffic to Adult Sites by Party (with covariates) 
%=============================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_visits} for the same plot without covariates.
	}
	\label{fig:quantile_regression_prop_visits_covariates}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Percentage Traffic to Adult Sites by Party (for individuals who consumed pornography)
%==============================================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (for individuals who consumed pornography)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_visits} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_visits_nonzeroes}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Percentage Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_visits_nonzeroes_covariates}
\end{figure}
